### 2023-08-23 chapter_2/src/appendix.qmd
update appendix to include treatments

>>>>

### Treatments

::: {#fig-treatments-trial1 layout-ncol=2}

![Red treatment](./study_1/assets/rep_yard_sign_round_1.png)
![Blue treatment](./study_1/assets/dem_yard_sign_round_1.png)
![White treatment](./study_1/assets/cont_yard_sign_round_1.png)

Trial 1 Treatments
:::

::: {#fig-treatments-trial2 layout-ncol=2}
![Red treatment](./study_1/assets//rep_yard_sign_round_2.png)
![Blue treatment](./study_1/assets/dem_yard_sign_round_2.png)
![White treatment](./study_1/assets/cont_yard_sign_round_2_3.png)

Trial 2 Treatments
:::

::: {#fig-treatments-trial3 layout-ncol=2}
![Red treatment](./study_1/assets/rep_yard_sign_round_3.png)
![Blue treatment](./study_1/assets/dem_yard_sign_round_3.png)
![White treatment](./study_1/assets/cont_yard_sign_round_2_3.png)

Trial 3 Treatments
:::

![Treatment example](./assets/img/example_of_treatment.png)
